\documentclass{article}
\title{NIUS BIOLOGY CAMP}
\author{Rahul Chavan}
\date{13 August 2023 }
\begin{document}
\maketitle
%adding the maketitle line will only add the title and author details to your document
%the star(*) after section will give a section title without any numbering

\section*{\underline{NIUS}}

NIUS stands for \textbf{\textit{National Initiative on Undergraduate Science }}, an initiative
of \textbf{HBCSE(TIFR)} for promoting undergraduate research and learning.
The NIUS student programme consists of an exposure cum enrichment camp 
with the central idea of exciting undergraduate students for basic sciences.

\section*{\underline{NIUS Biology}} 
The camp will comprise a combination of theory and lab sessions from reputed faculties in diverse fields of biology.
The focus of the sessions will be:
\begin{enumerate}
    \item Frontier research areas in the discipline
    \item Laboratory activities involving planning and decision making
    \item Comprehension of scientific literature 
    \item Problem solving
\end{enumerate}
The camp will also be a platform for like-minded students and mentors to connect.

\section*{\underline{Future prospects}}

Although being a part of the camp is a prestige in itself, there are also possibilities of future continuation.
 Select students will work on fascinating projects under the guidance of renowned faculties across the country for a tenure of over 1 year. 
 In the past, students have also got a chance to publish their work at the end of such projects.

\section*{\underline{Conclusion}}
All in all, the NIUS Biology Camp 2023-24 will be an invaluable opportunity to further cultivate my passion 
for biology, acquire new insights and develop practical skills which happen to be my major motivation to attend it.

\end{document}