\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic}  % 'casual' (default), 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}     % 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey', 'black'

% Adjust the page margins
\usepackage[scale=0.75]{geometry}


% Personal data
\name{Saksham Maitri}{}
%\title{B.Tech Mathematics and Computing}  % optional   
\address{Indian Institute of Science}{Bengaluru, 560012}{India}
\phone[mobile]{+91 8800786103}
\email{sakshamm@iisc.ac.in}
%\homepage{www.example.com}
%\social[twitter]{twitter.com/example}
%\social[linkedin]{linkedin.com/in/example}
\social[github]{Saksham-Maitri}
%\extrainfo{additional information}


\begin{document}

\makecvtitle

\section{Education}
\cventry{2023--2027}{B.Tech Mathematics and Computing}{Indian Institute of Science}{Bengaluru}{\textit{TGPA Semester 1 - 7.8/10}}{I am currently in my second semester}  % Arguments not required can be left empty
\cventry{2023}{Senior Secondary School (XII), Science}{School of Excellence}{Sec-17 Rohini, New Delhi}{(CBSE Board) Percentage: 93.0}{}
\cventry{2021}{Secondary School (X)}{School of Excellence}{Sec-17 Rohini, New Delhi}{(CBSE Board) Percentage: 90.8}{}





\section{Experience}

\cventry{Modelling using Machine Learning Data Sets}{}{}{}{}{Worked on various data sets and implemented machine learning models to predict the output.
The data sets were taken from Kaggle and UCI Machine Learning Repository.
Used Python libraries like Pandas, Numpy, Matplotlib, Seaborn, Scikit-learn, TensorFlow etc.
Experience in working with Neural Networks and Deep Learning.
Worked with CPLEX for optimization problems.
Implemented models like Linear Regression, Logistic Regression, Decision Trees, Random Forest, etc.}


\cventry{Canva}{}{}{}{}{Created various designs using Canva for social media posts, presentations, etc. for my college fests and for the Shutter Club at IISc }


\cventry{DSA and Competitive Programming}{}{}{}{}{Solved problems on various platforms like Codechef, LeetCode, etc. Participated in various contests on these platforms.
Solved problems on GeeksforGeeks and have a good understanding of Data Structures and Algorithms.
Here are links to my :
\begin{itemize}
    \item \href{https://www.codechef.com/users/sakshammaitri}{Codechef Profile}
    \item \href{https://leetcode.com/user9133dZ/}{LeetCode Profile}
\end{itemize}
}

\cventry{iGem Software and AI, IISc 2024}{}{}{}{}{I am a part of the iGem team at IISc, which is a team of undergraduate students working on a project to solve a real-world problem using Synthetic Biology.
We aim to use computational tools to solve problems in Biology.}


\cventry{Project Euler}{}{}{}{}{Solved problems on Project Euler. Project Euler is a collection of challenging problems in Mathematics and Computer Science.}


\section{Skills}
\cvitem{}{\textbf{Programming Languages}}
\cvitem{}{Python, C++, SQL}
\cvitem{}{\textbf{Tools}}
\cvitem{}{Git, LaTeX, Canva, Microsoft Office, Jupyter Notebook, Google Colab, Kaggle, etc.}
\cvitem{}{\textbf{Libraries}}
\cvitem{}{Pandas, Numpy, Matplotlib, Seaborn, Scikit-learn, TensorFlow, PyTorch etc.}



\section{Achievements/Awards}
\cvitem{2023}{Qualified for CMI Entrance Exam
CMI Entrance Exam is conducted by Chennai Mathematical Institute for admission to its B.Sc. (Hons.) in Mathematics and Computer Science and B.Sc. (Hons.) in Mathematics and Physics programs.}

\cvitem{2021}{Qualified for NTSE Scholarship
NTSE is a national-level scholarship program in India to identify and recognize students with high intellect and academic talent.}




\section{Languages}
\cvitemwithcomment{English}{Proficient}{}
\cvitemwithcomment{Hindi}{Fluent}{}


\section{Other interests}
\cvitem{Hobbies}{Photography, Reading, Sketching, etc.}
\cvitem{Others}{Physical Fitness, Sports, etc.}

%is there anything else i should add given that i am applying to a computing place where they expect me to code well and have a good understanding of mathematics and computing?


\clearpage

% If you want to include references
% \section{References}
% \cvitem{Name}{Reference details}
% \cvitem{Name}{Reference details}

\end{document}
